---
title: "Functions"
---

1. __What are the three components of a function?__  
* Envionment, arguments, and body.
```{r}
e <- new.env()
e$body <- print("Schrodinger's cat")
e$a <- function(argument){
  e$body
  if (argument < 0.5) {
    print('is dead.')
  } else {
    print('is alive.')
  }
}
print('Envionrment e variables:')
print(ls.str(e))
arg = runif(1)
sprintf('Calling function a in environment e with argument %.2f', arg)
e$a(arg)
```

2. __What does the following code return?__  
```{r}
x <- 10
f1 <- function(x) {
  function(y) {
    y + x + 10
  }
}
f1(1)(100)
```

3. __How would you more typically write this code?__
```{r}
`+`(1, `*`(2, 3))
```
* Answer:
```{r}
1 + (2* 3)
```

4. __How could you make this call easier to read?__  
```{r}
mean(, TRUE, x = c(1:10, NA))
```
* Answer:
```{r}
mean(c(1:10, NA), na.rm = TRUE)
```

5. __Does the following function throw an error when called? Why/why not?__  
```{r}
f2 <- function(a, b) {
  a * 10
}
f2(10, stop("This is an error!"))
```

* No, but we can pass the stop function if we want.
```{r, eval=FALSE}
f2 <- function(a, b) {
  a * 10
  b
}
f2(10, stop("This is an error!"))
```

6. __What is an infix function? How do you write it? What's a replacement function? How do you write it?__  
* An infix function combines arguments surrounding it. For example:
```{r}
`%blow_up%` <- function(a, b) a**b**a
print(5 %blow_up% 3)
```
* A replacement function can be defined and called as follows:
```{r}
# Must name second argument of replacement function "value"
"PIstep<-" <- function(a, value){
  a[a > 0.5] <- value
  a[a <= 0.5] <- 0
  print(a)
}

my_list = runif(10)
PIstep(my_list) <- 3.14
```
* `[` and `names` are examples of pre-defined replacement functions

7) __What function do you use to ensure that a cleanup action occurs regardless of how a function terminates?__  
* Call `on.exit()` at some point (best at start) of function. Stuff inside will be run upon exiting.
```{r}
neils_bohr <- function(){
  on.exit(print('father of QM'))
  print('A founding')
}
neils_bohr()
```

* My original answer was that deleted files can be removed by triggering "garbage collection"
```{r}
gc(verbose = TRUE)
```